Manuscript_Outputs

### 2024-02-10 Scripts/Stats_Analysis/RMarkdown/ManuscriptOutputs.Rmd
Tidy figures, save in format required for resubmission

export_svg(DiagrammeR::grViz(glue(gv))
           ) %>% charToRaw %>% rsvg %>%
  png::writePNG(here::here(file.path(config$outputs$figures, "Exclusions.png")))
```

@@

# plot Schoenfeld residuals
test.ph <- cox.zph(model_TC)
# test.ph
y <- test.ph$y
colnames(y) <- plot_varnames(colnames(y))
test.ph$y <- y
ggcoxzph(test.ph, point.alpha=0.04, var=c("Tyrer-Cuzick 10yr risk", "PRS_BC"),
         caption="Model also includes genetic array and first 4 principal components of genetic ancestry, plots omitted.")

@@

# plot Schoenfeld residuals
test.ph <- cox.zph(model_gail)
# test.ph
y <- test.ph$y
colnames(y) <- plot_varnames(colnames(y))
test.ph$y <- y
ggcoxzph(test.ph, point.alpha=0.04, var=c("Gail 10yr risk", "PRS_BC"),
         caption="Model also includes genetic array and first 4 principal components of genetic ancestry, plots omitted.")

@@

cal_plot <- function(data, var="TC_10risk", title, xlim=c(0, 0.1), ylim=c(0, 0.1)){

@@

  # Plot in calibration plot
  plot <- ggplot(calibration, aes(predicted, observed)) +
    geom_point(shape=22, size=3, color="blue", fill="blue") +
    geom_abline(aes(slope=1, intercept=0, linetype="dashed", colour="Ideal (y=x)"), show.legend=FALSE) +
    geom_smooth(method=lm, aes(colour="Best fit")) +
    geom_pointrange(aes(ymin=observed_lci, ymax=observed_uci)) +
    scale_x_continuous(limits=xlim) +
    scale_y_continuous(limits=ylim) +
    labs(x="Predicted risk",
         y="Observed risk",
         title=title) +
    annotate("text", x=0.05, y = 0.02, size=10/.pt,
             label=paste0("Slope = ", pretty_dp(cal_slope, 3), 
                          "\nIntercept = ", pretty_dp(cal_intercept, 3))) +
    scale_color_manual(name = "Legend",             # legend name
                     values = c("Ideal (y=x)" = "black",  # map regression line colors
                                "Best fit" = "blue")) +
    theme(legend.justification = c(0, 1), legend.position = c(0, 1)) +
    theme(plot.title = element_text(size=10))

  ggsave(file.path(config$outputs$figures, paste0(var, "_calibration_plot10.jpg")), 
       scale=0.6, width=25, height=15, units="cm")

@@

# 2. Save the legend
#+++++++++++++++++++++++
legend <- get_legend(TC_train$plot)
# 3. Remove the legend
#+++++++++++++++++++++++
gridExtra::grid.arrange(TC_train$plot + theme(legend.position="none"), 
                        gail_train$plot + theme(legend.position="none"), 
                        legend, 
                        TC_test$plot + theme(legend.position="none"), 
                        gail_test$plot + theme(legend.position="none"),
                        NULL,
                        TC_prs_cal$plot + theme(legend.position="none"),
                        gail_prs_cal$plot + theme(legend.position="none"),
                        ncol=3, widths=c(3.5, 3.5, 0.8))

@@

  tROC_long <- rbind(cbind(tROC[[1]][["TP"]], tROC[[1]][["FP"]]),
                     cbind(tROC[[2]][["TP"]], tROC[[2]][["FP"]]),
                     cbind(tROC[[3]][["TP"]], tROC[[3]][["FP"]]))
  colnames(tROC_long) <- c("TP_9", "TP_10", "FP_9", "FP_10")
  tROC_df <- data.frame(tROC_long)
  tROC_df$Model <- factor(c(rep(paste0(modelname, " 10-yr risk"), times=dim(tROC[[1]][["TP"]])[1]),
                     rep(paste0(prsname, " PRS"), times=dim(tROC[[2]][["TP"]])[1]),
                     rep(paste0(modelname, " & PRS 10-yr risk"), times=dim(tROC[[3]][["TP"]])[1])),
                     levels=c(paste0(modelname, " 10-yr risk"),
                              paste0(prsname, " PRS"),
                              paste0(modelname, " & PRS 10-yr risk")))

  plot <- ggplot(tROC_df,aes(x=FP_10, y=TP_10, color=Model))+
    geom_line(linewidth=1) + style_roc() +
    geom_abline(aes(slope=1, intercept=0), linetype="dashed") +
    xlab("False positive fraction") + ylab("True positive fraction") +
    scale_color_manual(name="Model",values = c("#F8766D","#00BA38", "#6193FF")) +
    labs(title =plotname, caption = "Dashed line is y=x")+
    theme(legend.position = c(0.75, 0.15))

  ggsave(file.path(config$outputs$figures, paste0("rocplot_", modelname, ".jpg")),
       scale=0.7, width=25, height=15, units="cm")

@@

# Tyrer-Cuzick
TC_roc <- td_roc_plot(test_data, modelname="TC", prsname="Genomics plc", plotname="Tyrer-Cuzick",
         varlist=c("TC_10risk_cal", "PRS_bc_std", "TC_prs_10risk"))

# Gail
gail_roc <- td_roc_plot(test_data, modelname="Gail", prsname="Genomics plc", plotname="Gail",
         varlist=c("gail_10risk_cal", "PRS_bc_std", "gail_prs_10risk"))

gridExtra::grid.arrange(TC_roc, gail_roc,
                        ncol=2,
                        top=paste0("Time-dependent ROC curves at 10 years follow up in test data (N=", nrow(test_data), ")"))

@@

dca_tc
ggsave(file.path(config$outputs$figures, "TC_DCA.png"), 
       scale=0.7, width=25, height=15, units="cm")

@@

dca_gail
ggsave(file.path(config$outputs$figures, "gail_DCA.png"), 
       scale=0.7, width=25, height=15, units="cm")

gridExtra::grid.arrange(dca_tc, dca_gail,
                        ncol=2,
                        top=paste0("Decision curves for 10-year risk from models with and without PRS_BC in test data (N=",
                                   nrow(test_data), ")"))

@@

ia_tc
ggsave(file.path(config$outputs$figures, "TC_NIA.png"), 
       scale=0.7, width=25, height=15, units="cm")

@@

ia_gail
ggsave(file.path(config$outputs$figures, "gail_NIA.png"), 
       scale=0.7, width=25, height=15, units="cm")

gridExtra::grid.arrange(ia_tc, ia_gail,
                        ncol=2,
                        top=paste0("Net interventions avoided per 100 women for 10-year risk from models with and without PRS_BC in test data (N=",
                                   nrow(test_data), ")"))

@@

facet_data <- test_data %>% select(TC_10risk_cal, TC_prs_10risk, TEU_BrCa_status) %>% 
  pivot_longer(cols=c(TC_10risk_cal, TC_prs_10risk))

density_data <- facet_data %>%
  mutate(
    name = ifelse(TEU_BrCa_status == 0, paste0(name, "_control"), paste0(name, "_case")),
    Model = factor(name, 
                   levels=c("TC_10risk_cal_control", "TC_10risk_cal_case",
                            "TC_prs_10risk_control", "TC_prs_10risk_case"),
                   labels = c("Tyrer-Cuzick controls", "Tyrer-Cuzick cases",
                              "Tyrer-Cuzick with PRS_BC controls", "Tyrer-Cuzick with PRS_BC cases")))

ggplot(density_data, 
       aes(x=value, fill=Model)) + 
  geom_density(alpha=0.4, position="identity") +
  ggtitle("Density plot of 10yr predicted risk by model in test data, split by cases and controls") +
  theme(legend.position = c(0.8, 0.8)) +
  xlim(0, 0.2) +
  geom_vline(xintercept=0.05)

ggsave(file.path(config$outputs$figures, "TC_density_10yrrisk.png"), 
       scale=0.7, width=25, height=15, units="cm")

facet_data <- test_data %>% select(gail_10risk_cal, gail_prs_10risk, TEU_BrCa_status) %>% 
  pivot_longer(cols=c(gail_10risk_cal, gail_prs_10risk))

density_data <- facet_data %>%
  mutate(
    name = ifelse(TEU_BrCa_status == 0, paste0(name, "_control"), paste0(name, "_case")),
    Model = factor(name, 
                   levels=c("gail_10risk_cal_control", "gail_10risk_cal_case",
                            "gail_prs_10risk_control", "gail_prs_10risk_case"),
                   labels = c("Gail controls", "Gail cases",
                              "Gail with PRS_BC controls", "Gail with PRS_BC cases")))

ggplot(density_data, 
       aes(x=value, fill=Model)) + 
  geom_density(alpha=0.4, position="identity") +
  ggtitle("Density plot of 10yr predicted risk by model in test data, split by cases and controls") +
  theme(legend.position = c(0.8, 0.8)) +
  xlim(0, 0.2) +
  geom_vline(xintercept=0.05)

ggsave(file.path(config$outputs$figures, "Gail_density_10yrrisk.png"), 
       scale=0.7, width=25, height=15, units="cm")

>>>>

# Supplementary Figure 1

export_svg(DiagrammeR::grViz(glue(gv))) %>% 
  charToRaw %>% 
  rsvg %>%
  png::writePNG(here::here(file.path(config$outputs$figures$final, "SuppFigureS1.png")))

@@

# plot Schoenfeld residuals
test.ph <- cox.zph(model_TC)
# test.ph
y <- test.ph$y
colnames(y) <- plot_varnames(colnames(y))
test.ph$y <- y

# Supplementary Figure 3
tiff(file.path(config$outputs$figures$final,"SuppFigureS3.tiff"), units="in", width=8, height=5, res=300)
ggcoxzph(test.ph, point.alpha=0.04, var=c("Tyrer-Cuzick 10yr risk", "PRS_BC"),
         caption="Model also includes genetic array and first 4 principal components of genetic ancestry, plots omitted.")
dev.off()

@@

# plot Schoenfeld residuals
test.ph <- cox.zph(model_gail)
# test.ph
y <- test.ph$y
colnames(y) <- plot_varnames(colnames(y))
test.ph$y <- y

# Supplementary Figure 4
tiff(file.path(config$outputs$figures$final,"SuppFigureS4.tiff"), units="in", width=8, height=5, res=300)
ggcoxzph(test.ph, point.alpha=0.04, var=c("Gail 10yr risk", "PRS_BC"),
         caption="Model also includes genetic array and first 4 principal components of genetic ancestry, plots omitted.")
dev.off()

@@

cal_plot <- function(data, var="TC_10risk", title, xlim=c(0,0.1), ylim=c(0,0.1)){

@@

  # Plot in calibration plot
  plot <- ggplot(calibration, aes(predicted, observed)) +
    geom_point(shape=22, size=3, color="blue", fill="blue") +
    geom_abline(aes(slope=1, intercept=0, linetype="dashed", colour="Ideal (y=x)"), show.legend=FALSE) +
    geom_smooth(method=lm, aes(colour="Best fit")) +
    geom_pointrange(aes(ymin=observed_lci, ymax=observed_uci)) +
    scale_x_continuous(limits=xlim) +
    scale_y_continuous(limits=ylim) +
    labs(x="Predicted risk",
         y="Observed risk",
         title=title) +
    annotate("text", x=0.07, y = 0.015, size=10/.pt,
             label=paste0("Slope = ", pretty_dp(cal_slope, 3), 
                          "\nIntercept = ", pretty_dp(cal_intercept, 3))) +
    scale_color_manual(name = "Legend",             # legend name
                     values = c("Ideal (y=x)" = "black",  # map regression line colors
                                "Best fit" = "blue")) +
    theme(legend.justification = c(0, 1), legend.position = c(0, 1)) +
    theme(plot.title = element_text(size=10))

  ggsave(file.path(config$outputs$figures$interim, paste0(var, "_calibration_plot10.jpg")), 
       scale=0.6, width=25, height=15, units="cm")

@@

# 2. Save the legend
#+++++++++++++++++++++++
legend <- get_legend(TC_train$plot)
# 3. Remove the legend
#+++++++++++++++++++++++
# Figure 1
tiff(file.path(config$outputs$figures$final,"Figure1.tiff"), units="in", width=8, height=10, res=300)
gridExtra::grid.arrange(TC_train$plot + theme(legend.position="none"), 
                        gail_train$plot + theme(legend.position="none"), 
                        legend, 
                        TC_test$plot + theme(legend.position="none"), 
                        gail_test$plot + theme(legend.position="none"),
                        NULL,
                        TC_prs_cal$plot + theme(legend.position="none"),
                        gail_prs_cal$plot + theme(legend.position="none"),
                        ncol=3, widths=c(3.5, 3.5, 1))
dev.off()

@@

  tROC_long <- rbind(cbind(tROC[[1]][["TP"]], tROC[[1]][["FP"]]),
                     cbind(tROC[[2]][["TP"]], tROC[[2]][["FP"]]),
                     cbind(tROC[[3]][["TP"]], tROC[[3]][["FP"]]))
  colnames(tROC_long) <- c("TP_9", "TP_10", "FP_9", "FP_10")
  tROC_df <- data.frame(tROC_long)
  tROC_df$Model <- factor(c(rep(paste0(modelname, " 10-yr risk"), times=dim(tROC[[1]][["TP"]])[1]),
                     rep(prsname, times=dim(tROC[[2]][["TP"]])[1]),
                     rep(paste0(modelname, " & PRS_BC 10-yr risk"), times=dim(tROC[[3]][["TP"]])[1])),
                     levels=c(paste0(modelname, " 10-yr risk"),
                              prsname,
                              paste0(modelname, " & PRS_BC 10-yr risk")))

  plot <- ggplot(tROC_df,aes(x=FP_10, y=TP_10, color=Model))+
    geom_line(linewidth=1) + style_roc() +
    geom_abline(aes(slope=1, intercept=0), linetype="dashed") +
    xlab("False positive fraction") + ylab("True positive fraction") +
    scale_color_manual(name="Model",values = c("#F8766D","#00BA38", "#6193FF")) +
    labs(title =plotname, caption = "Dashed line is y=x")+
    theme(legend.position = c(0.7, 0.15))

  ggsave(file.path(config$outputs$figures$interim, paste0("rocplot_", modelname, ".jpg")),
       scale=0.7, width=25, height=15, units="cm")

@@

# Tyrer-Cuzick
TC_roc <- td_roc_plot(test_data, modelname="Tyrer-Cuzick", prsname="PRS_BC", plotname="Tyrer-Cuzick",
         varlist=c("TC_10risk_cal", "PRS_bc_std", "TC_prs_10risk"))

# Gail
gail_roc <- td_roc_plot(test_data, modelname="Gail", prsname="PRS_BC", plotname="Gail",
         varlist=c("gail_10risk_cal", "PRS_bc_std", "gail_prs_10risk"))

# Figure 2
tiff(file.path(config$outputs$figures$final,"Figure2.tiff"), units="in", width=10, height=5, res=300)
gridExtra::grid.arrange(TC_roc, gail_roc,
                        ncol=2)
dev.off()

@@

dca_tc
ggsave(file.path(config$outputs$figures$interim, "TC_DCA.png"), 
       scale=0.7, width=25, height=15, units="cm")

@@

dca_gail
ggsave(file.path(config$outputs$figures$interim, "gail_DCA.png"), 
       scale=0.7, width=25, height=15, units="cm")

# Figure 3
tiff(file.path(config$outputs$figures$final,"Figure3.tiff"), units="in", width=10, height=5, res=300)
gridExtra::grid.arrange(dca_tc, dca_gail, ncol=2)
dev.off()

@@

ia_tc
ggsave(file.path(config$outputs$figures$interim, "TC_NIA.png"), 
       scale=0.7, width=25, height=15, units="cm")

@@

ia_gail
ggsave(file.path(config$outputs$figures$interim, "gail_NIA.png"), 
       scale=0.7, width=25, height=15, units="cm")

gridExtra::grid.arrange(ia_tc, ia_gail, ncol=2)

@@

# Tyrer-Cuzick
facet_tc <- test_data %>% select(TC_10risk_cal, TC_prs_10risk, TEU_BrCa_status) %>% 
  pivot_longer(cols=c(TC_10risk_cal, TC_prs_10risk))

density_data_tc <- facet_tc %>%
  mutate(
    name = ifelse(TEU_BrCa_status == 0, paste0(name, "_control"), paste0(name, "_case")),
    Model = factor(name, 
                   levels=c("TC_10risk_cal_control", "TC_10risk_cal_case",
                            "TC_prs_10risk_control", "TC_prs_10risk_case"),
                   labels = c("Tyrer-Cuzick controls", "Tyrer-Cuzick cases",
                              "Tyrer-Cuzick with PRS_BC controls", "Tyrer-Cuzick with PRS_BC cases")))

density_TC <- ggplot(density_data_tc, 
       aes(x=value, fill=Model)) + 
  geom_density(alpha=0.4, position="identity") +
  theme(legend.position = c(0.8, 0.8)) +
  xlim(0, 0.2) +
  geom_vline(xintercept=0.05)

# Gail
facet_gail <- test_data %>% select(gail_10risk_cal, gail_prs_10risk, TEU_BrCa_status) %>% 
  pivot_longer(cols=c(gail_10risk_cal, gail_prs_10risk))

density_data_gail <- facet_gail %>%
  mutate(
    name = ifelse(TEU_BrCa_status == 0, paste0(name, "_control"), paste0(name, "_case")),
    Model = factor(name, 
                   levels=c("gail_10risk_cal_control", "gail_10risk_cal_case",
                            "gail_prs_10risk_control", "gail_prs_10risk_case"),
                   labels = c("Gail controls", "Gail cases",
                              "Gail with PRS_BC controls", "Gail with PRS_BC cases")))

density_gail <- ggplot(density_data_gail, 
       aes(x=value, fill=Model)) + 
  geom_density(alpha=0.4, position="identity") +
  theme(legend.position = c(0.8, 0.8)) +
  xlim(0, 0.2) +
  geom_vline(xintercept=0.05)

# Supplementary Figure 5
tiff(file.path(config$outputs$figures$final,"SuppFigureS5.tiff"), units="in", width=8, height=10, res=300)
gridExtra::grid.arrange(density_TC, density_gail, nrow=2)
dev.off()
